---
title: "Alcohol vs Seat choice"
author: "Edward Gomez"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

More people sit in the middle than in the front and back combined. There are slightly more people in the front than in the back. The mean of the amount of alcohol consumed by each group is as follows: The back leading strongly with 8.555556, the middle with 6.225381, and the front with the least, being 1.787500.
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

I found the p-value to be 0.000116. This value is small enough to show that there may be a significant statistical difference.

```{r}
plot(TukeyHSD(model1))
```

Looking at the 95% confidence interval one can see if there is a significant statistical difference between each group. Since the Middle-Back and Front-back intervals do not lie on 0 they are statistically different. The Middle-Front does lie on zero, which means there is not a statistical difference. 

##Conclusions 

I learned that while having only two categories of data is similar to multiple categories, there are additional steps that must be taken for the latter. It started the same with plotting the data using box plots, as well as finding the standard deviation and the mean. After that I found the the p-value and found it to be small enough to be significant. This is where I took the additional steps to use "one way anova" to compare the categories against each other. This showed me a 95% confidence interval that showed the Middle-Back and Front-Back were significantly different while the Middle-Front was not significantly different due to having 0 as part of the interval.