---
title: "Alcohol vs Seat choice"
author: "Edward Gomez"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

More people sit in the middle than in the front and back combined. There are slightly more people in the front than in the back. The mean of the amount of alcohol consumed by each group is as follows: The back leading strongly with 8.555556, the middle with 6.225381, and the front with the least, being 1.787500.
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

I found the p-value to be 0.000116. This value is small enough to show that there may be a significant statistical difference.

```{r}
plot(TukeyHSD(model1))
```

Looking at the 95% confidence interval one can see if there is a significant statistical difference between each group. Since the Middle-Back and Front back intervals do not lie on 0 they are statistically different. The Middle-Front does lie on zero, which means there is not a statistical difference. 

## Conclusions

